---
title: "BiocHFhub: Accessing biological pretrained models from HuggingFace"
author:
- name: Ilaria Billato
  affiliation: [
    "Department of Biology, University of Padova"
  ]
date: "`r Sys.Date()`"
output:
  BiocStyle::html_document:
    toc: true
    number_sections: true
    toc_float: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Using BiocHFhub for Biological Data Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(BiocHFhub)
```

# Introduction

The **BiocHFhub** package provides an interface between Bioconductor 
and the Hugging Face Hub for biological data analysis. 
It allows users to list, download, and extract parameters from 
pretrained models for analyzing protein sequences, omics data, 
and histology images.

# List Available Models

```{r list-models}
models <- list_hfbio_models()
print(models)
```

You can also filter models by task, for example, to show only models for 
protein embedding:

```{r filter-models}
protein_models <- list_hfbio_models(task = "Protein Embedding")
print(protein_models)
```

# Download a Model File

You can download specific files (e.g., configuration files) 
from a model repository:

```{r download-model}
config_path <- download_hfbio_model("facebook/esm2_t33_650M_UR50D", 
                                    filename = "config.json")
print(config_path)
```

# Read Model Parameters

You can easily load and inspect model parameters:

```{r get-parameters}
params <- get_hfbio_model_parameters("facebook/esm2_t33_650M_UR50D")
str(params)
```

# Conclusion

**BiocHFhub** simplifies the connection between R/Bioconductor and 
state-of-the-art pretrained models on Hugging Face, empowering biological 
researchers with modern machine learning tools.

# Session Info

<details>
    <summary>Click here for Session Info</summary>
```{r}
sessionInfo()
```
</details>
